Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for Collaborative Interactive Learning Techniques

### 2018-08-21 paper.tex
Extend section 2: COLLABORATIVE INTERACTIVE LEARNING

\section{Collaborative Interactive Learning}\label{sec:cil}
\notes{[More detail.]}
CIL includes domain experts (humans) 
and other CIL systems in the decision/prediction making process as shown in 
Figure~\ref{fig:CIL}. The relatively new term describes a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and the one of other entities in a 
        bi-directional way\cite{CIL:sick}.
\end{itemize}
\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{images/CIL}
\caption{Interaction between heterogeneous systems in CIL.}
\label{fig:CIL}
\end{figure}

@@

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.
\notes{[Add examples for each classification.]}

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and used in a variety of applications 
where labeled data is easy to obtain. The spam mail example discussed in the introduction is a 
case of supervised learning.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner here receives only 
unlabeled training data and makes predictions for all unseen points. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
\notes{[Maybe Clustering as an example.]}

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabelled data and makes predictions for all unseen points.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is expensive.
\notes{[Example needed.]}

@@

\begin{itemize}
    \item \textit{Text classification, Natural Language Processing (NLP)}. 
        Many current mail programs have built-in spam detection which originally used
        simple regular expressions in order to detect phrases commonly used in spam mails.
        With state-of-the-art ML techniques it is not only possible for a mail program to 
        query for a number of words but to recognise patterns of how spam mails are constructed and 
        to adapt itself to new types of spam.
    \item \textit{Speech recognition}. 
        Most commercial applications for speech recognition also use ML to train itself to 
        recognise a user's speech input in order to perform further semantic analysis on
        that data.
    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifying 
        objects or recognizing handwritten characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses
        \cite{DisciplineOfML:mitchell}.
    \item \textit{Games}.
        Computer Games usually offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a relatively small game tree containing 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents, modern Games are using ML to gain experience 
        by themselves.
    \item \textit{Search engines, Recommendation systems}.
        Nearly all current search machines use ML in one fashion or another. They mainly use these 
        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
        search results and for \textit{(2) Query classification} in order to ``understand' a 
        users query and to provide further meaningful information.
\end{itemize}

@@

@@

So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see section~\ref{sec:intro}) in finding solutions (for example by excluding unpromising folds).

>>>>

\section{Collaborative Interactive Learning}\label{sec:cil}
The term \textit{Collaborative Interactive Learning (CIL)} is a relatively new concept of systems which 
includes other domain experts (humans) and CIL systems in the decision/prediction making process 
as shown in Figure~\ref{fig:CIL}. It describes the vision of a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base (\textit{learning})
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and learning process and the one of other entities in a 
        bi-directional way (\textit{interactive}, \textit{collaborative})\cite{CIL:sick}.
\end{itemize}
\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{images/CIL}
\caption{Interaction between heterogeneous systems in CIL.\notes{own work}}
\label{fig:CIL}
\end{figure}
So the main difference to classical ML is the possibilty to adapt and optimize itself during run-time 
towards new situations without having been specifically trained for these use-cases whereas classical ML 
systems have had to be fed with a sufficient amount of relevant training data\cite{CIL:sick}\cite{Organic:schloer}.
Furthermore, CIL systems interact with their environment in order to not rely on a single training data set. 
They collect data from several other systems (including humans) to validate already existing information and to 
gather additional data from other sources. In this way, CIL systems can be used in a lot of application areas where 
environments are constantly changing or training data is rarely available.

@@

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and used in a variety of applications 
where labeled data is easy to obtain. The spam mail example discussed in the introduction is a 
case of supervised learning.
Many current mail programs have built-in spam detection which originally used
simple regular expressions in order to detect phrases commonly used in spam mails.
With state-of-the-art ML techniques it is not only possible for a mail program to 
query for a number of words but to recognise patterns of how spam mails are constructed and 
to adapt itself to new types of spam.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner receives only 
unlabeled training data and makes predictions for all unseen points in this concept. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
They mainly use these techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
search results and for \textit{(2) Query classification} in order to ``understand' a 
users query and to provide further meaningful information. 
\notes{[not sure if unsupervised; clustering and dimensionality reduction however is.]}

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabelled data and makes predictions for all unseen points.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is expensive.
Most commercial applications for speech recognition are using this technique to train itself to 
recognise a user's speech input in order to perform further semantic analysis on
that data. \notes{[not sure if unsupervised]}
\notes{[Example needed.]}

@@

\begin{itemize}
    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifying 
        objects or recognizing handwritten characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses
        \cite{DisciplineOfML:mitchell}.
    \item \textit{Games}.
        Computer Games usually offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a relatively small game tree containing 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents, modern Games are using ML to gain experience 
        by themselves.
\end{itemize}

@@

\subsection{Self-Configuration}
\subsection{Self-Optimization}
\subsection{Self- Healing and Protecting}
\subsection{Self-Explanatory}

@@

So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see Section~\ref{sec:intro}) in finding solutions 
for example by excluding unpromisingfls.
